Two-component thermal dust emission model: application to the {\it PLANCK} HFI maps

### 2014-01-25 ms.tex
outlining

\begin{equation}
\sigma_{\nu_i} = \sqrt{c^2_{\nu_i}I^2_{\nu_i} + c^2_{\nu_i}CMB^2_{\nu_i} + (\delta O_{\nu_i})^2 + n^2_{\nu_i}}
\end{equation}

@@

@@

@@

%provide maps at multiple different nsides ?
%   -> if so, actually smooth the maps before rebinning, or leave 
%      undersampled?
% provide uncertainty maps for tau and T2 ??

\subsection{Limitations}
Perhaps the dominant limitation of our fits is the presence of cosmic
infrared background anisotropies (CIBA) bleeding through into our maps of 
Galactic dust temperature and optical depth in high-latitude regions 
\citep{ciba}.
% CIBA !!!
% IRAS missing so that parts of sky not truly 6.1' resolution map

@@

\subsubsection{Omitting 217 GHz}
The \cite{planckdust} result used only 353, 545, 857, and 3000 GHz. When we 
repeat our analysis ignoring 217 GHz, so that we are using the same
set of frequencies, we find that no major changes arise. This actually
should be done/investigated though.

>>>>

\begin{equation}
\sigma_{\nu_i}(p) = \sqrt{c^2_{\nu_i}I_{\nu_i}(p)^2 + c^2_{\nu_i}CMB(p)^2 + (\delta O_{\nu_i})^2 + n_{\nu_i}(p)^2}
\end{equation}

@@

\subsection{Low Resolution Fits}
%mention that the pixelization changes ---> to lower HEALpix nside
%mention that over some region of the sky with high signal and high
%S/N we try fitting t2, normalization and one of q1/q2, f_1
%using more bands (including 143, and maybe 100 GHz)

\section{Systematics}

\subsection{CIBA}
Perhaps the dominant limitation of our fits is the presence of cosmic
infrared background anisotropies (CIBA) bleeding through into our maps of 
Galactic dust temperature and optical depth in high-latitude regions 
\citep{ciba}.
\subsubsection{Simulations}

\subsubsection{Optimizing Relative Weights}

%not sure if below subsection is necessary, idea of giving zero weight to 217 
%GHz may belong in above subsection

%\subsubsection{Omitting 217 GHz}
%The \cite{planckdust} result used only 353, 545, 857, and 3000 GHz. When we 
%repeat our analysis ignoring 217 GHz, so that we are using the same
%set of frequencies, we find that no major changes arise. This actually
%should be done/investigated though.

\subsection{Zero Point}
Simulate the effect of getting zero points wrong to quantiy this
systematic a bit.

\subsection{$T_{2}$ Prior}
Use FIRAS data to justify $T_2$ prior.

\subsection{Other Limitations}
\IRAS~is missing in some parts of sky which will therefore not truly have 6.1' 
resolution.
%any other miscellaneous issues?

@@

% this subsection should probably be moved to the ``dust emission model'' 
% section of the paper eventually

@@

%software utilities
%provide maps at multiple different nsides ?
%   -> if so, actually smooth the maps before rebinning, or leave 
%      undersampled?
% provide uncertainty maps for tau and T2 ??

@@

\subsection{Validation with FIRAS}
